\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-23 paper/manuscript.tex
final section revision
explanation for the use of a webdriver-controlled browser and wget

To test whether the websites we found actually work, we use a webdriver-controlled browser [@markus, please define ``webdriver-controlled''] (Firefox/Selenium/Geckodriver). This is necessary because a) some city websites simply don't work  [@markus, why is it advantageous to use a webdriver-controlled browser for when a city website doesn't work?], and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL. A webdriver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection. This allows us to subsequently record and use the new URL for the actual website scraping. [@markus, would you add a few sentences documenting what we did to scrape the web files (i.e., used wget). Considering this section and the next one, its not clear how you get from a list of tested URLs to the website files being on your hard drive]. For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results. Consequently we restricted our corpus to cities with at least 3 documents.

@@

% BRUCE HERE
\begin{itemize}
\item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two. This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us, but are very effective at differentiating cities. These terms also happen to be fairly common, which causes them to be overweighted by the topic model.

>>>>

To test whether the websites we found actually work, we use a webdriver-controlled browser - a browser that is automatically controlled by a program rather than a human user. We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the webdriver  \texttt{Geckodriver}. This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers. Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection. Scrapers can perform most, but not all of such operations. The use of a webdriver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL. A webdriver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection. This allows us to subsequently record and use the new URL for the actual website scraping. Consequently, an automated browser allows us to robustly answer the following questions: Is the website actually there? Does it work? If not, is it somewhere else or is it broken? We record this information and construct a list of verified URLs.

To download the websites, we rely on the Unix command line tool \texttt{wget}. This program is used to download files from the Internet, and with the use of a recursive option, acts like a webcrawler and scraper. This means that \texttt{wget} scrapes HTML files, parses them and then follows the links contained therein. Then it follows those links, and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain). This way, all the files that make up a website are downloaded. For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results. Consequently we restricted our corpus to cities with at least 3 documents.

@@

\begin{itemize}
\item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two. This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us, but are very effective at differentiating cities. These terms also happen to be fairly common, which causes them to be overweighted by the topic model.
